RUPEE: A fast and accurate purely geometric protein structure search

### 2019-01-29 docs/rupee_2.tex
fix reference

Figures similar to \figurename~\ref{fig:combined_scoring_tm_avg} but instead using CE and FATCAT for pairwise comparisons can be found in \nameref{S2_Fig} \nameref{S3_Fig}, respectively. 
These additional figures lend further support to what has already been show above.

@@

\paragraph*{S2 Fig.}
\label{S2_Fig}
{\bf Scoring from FATCAT pairwise alignments.}

>>>>

Figures similar to \figurename~\ref{fig:combined_scoring_tm_avg} but instead using CE and FATCAT for pairwise comparisons can be found in \nameref{S2_Fig} and \nameref{S3_Fig}, respectively. 
These additional figures lend further support to what has already been show above.

@@

\paragraph*{S2 Fig.}
\label{S2_Fig}
{\bf Scoring from CE pairwise alignments.}

\paragraph*{S3 Fig.}
\label{S3_Fig}
{\bf Scoring from FATCAT pairwise alignments.}
